%% start of file `resume_en.tex'.

\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
\moderncvtheme[grey]{classic}                 
% optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)

%\moderncvtheme[green]{classic}                % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\recomputelengths                             % required when changes are made to page layout lengths

% personal data
\firstname{Rafael}
\familyname{Lopes}
\title{Software Developer}                    % optional, remove the line if not wanted
\mobile{(+55-11) 6729-1897}                    % optional, remove the line if not wanted
\email{rafaellg@vision.ime.usp.br}                      % optional, remove the line if not wanted
\extrainfo{\href{http://br.linkedin.com/in/rafaelolg}{http://br.linkedin.com/in/rafaelolg}} % optional, remove the line if not wanted

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle
%\section{Objective}
%\cvline{}{My objective}

\section{Education}

\cventry{2010 -- 2013}{Master of Science}{University of São Paulo}{São Paulo}{Institute of Mathematics and Stastistics}{ 
Research Area: Computer Vision and Image Processing.
\newline{Supervisor:}  Prof. Dr. Roberto Hirata.
}

\cventry{2004--2009}{Bacharel (4-Year Bachelor) in Computer Science}{University of São Paulo}{Institute of Mathematics and Stastistics}{São Paulo}{}

\section{Experience}
\cventry{2012 -- Present}{Developer}{\href{http://www.artis.com.br/eximius/index\_eximius.php}{Artis}}{São Paulo}{}{
Development of neural navigator for computer assisted medical image visualization in surgery;
\newline{} Computer vision and computer graphics application in python using VTK.
\newline{} Technical lead of a small team.
}

\cventry{2011 -- 2012}{Project Analyst}{\href{http://www.nic.br}{Nic.br}}{São Paulo}{}{
    Development of technologies to measure broadband internet quality. 
\newline{} Data analysis of results from tests, dealing with huge datasets.
\newline{} Creation of automatic network failure detection using machine learning.
\newline{} Development of a webservice for distributed data storage.
\newline{} Working with C(embedded), Java and Python(for data analysis) systems.
\newline{} Project: \href{http://simet.nic.br}{Simet.nic.br}.
}

\cventry{2010 -- 2011}{Software Developer}{\href{http://www.whitehat.com.br}{WhiteHat}}{São Paulo}{}{Development of Django Python applications. 
\newline{} Development of django web systems.
\newline{} Creation of a webscrapper to extract data from online social networks in python.
}

\cventry{2007 -- 2009}{Intern in Software Development}{\href{http://www.pra.com.br}{PR\&A}}{São Paulo}{}{Development of financial software. 
\newline{} Technologies used include Java Server Faces, Spring, Maven and JPA.}


\cventry{2007 -- 2007}{Intern in Software Development}{\href{http://www.lsitec.org.br}{LSITEC}}{São Paulo}{}{Development of embedded software using C language.
\newline{} Cellphone development.
\newline{} Interaction with co-workers overseas.}


\cventry{2005 -- 2007}{Sysadmin}{\href{http://www.linux.ime.usp.br}{ Rede Linux-IME-USP}}{São Paulo}{}{Maintenance of a Linux based network with over 100 computers and
more than 3000 users, using only free software.}


\section{Computer related skills}
\cvline{Languages}{C, Java, Python, SQL,  and good notions of R and C++.}
\cvline{Markup}{HTML, CSS and \LaTeX.}
\cvline{Version Control Systems}{GIT, Mercurial and Subversion}
\cvline{Platforms}{Linux, Unix and Windows}
\cvline{Tools}{Vim, GCC, Make, Autotools, Maven.}
\cvline{Frameworks Python}{Django, OpenCV, Numpy, Vtk, Wx, Reportlab and Celery.}
\cvline{Frameworks J2EE}{Spring, Hibernate and EJB.}
\cvline{C Libraries}{Pthreads, Sockets, OpenGL,  OpenCV.}

\section{Languages}
\cvline{Portuguese}{Native Language.}
\cvline{English}{Speaking, reading, and writing.}

\section{Research Interests}
\cvlistitem{Computer vision.}
\cvlistitem{Human color vision.}
\cvlistitem{Machine learning and Data analysis.}
\cvlistitem{Web Development}

\section{General Interests}
\cvline{Open Source Projects Collaborations}{
\href{bitbucket.org/rafaellg/visiondataset}{bitbucket.org/rafaellg/visiondataset} --- A web platform for scientific collaboration;
\newline{} \href{visocor.sourceforge.net}{visocor.sourceforge.net} --- A Compiz plugin for colorblindness accessibility.
\newline{} \href{github.com/rafaelolg/salienpy}{github.com/rafaelolg/salienpy} --- Salienpy is a set of state of the art saliency models implementations in python.}


\closesection{}                   % needed to renewcommands
\renewcommand{\listitemsymbol}{-} % change the symbol for lists

% Publications from a BibTeX file
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}       % 'publications' is the name of a BibTeX file

\end{document}

